\textbf{Resilient Machine Learning Approaches \\ for Fast Risk Evaluation and Management \\ of Financial Portfolios and Variable Annuities}

### 2025-04-02 pre_private/pre.tex
1

\note{In the context of quantitative risk management, nested simulation is used for risk evaluation of financial derivatives and insurance products. \\}
\note{The nested structure is due to the loss random variable being a conditional expectation of the portfolio loss given the underlying risk factors. \\}
\note{In our problems, the loss $L$ depends on the risk factors $X$ and is the conditional expectation of the portfolio loss given the risk factors. \\}
\note{More specifically, $X$ is $d$-dimensional and $L$ is 1-dimensional. \\}
\note{Estimating a risk measure, $\rho(L)$, involves two levels of Monte Carlo simulations: a outer level generates underlying risk factors, and a inner level generates scenario-wise samples of portfolio losses. \\}
\note{The standard nested simulation procedure uses the inner sample mean under that scenarioto estimate $L(X_i)$. \\}
\note{The nested structure makes the estimation computationally expensive. \\}
\note{In this thesis, we focus on examining and improving the efficiency of nested simulation procedures mostly by pooling with supervised learning metamodels.}

@@

\note{Pooling can happen in different ways, and the key idea is to use the information from different outer scenarios to improve the efficiency of nested simulation. \\}
\note{A supervised learning based nested simulation procedure pools with these steps. \\}
\note{First, the user runs the standard nested simulation procedure to generate a set of outer scenarios and inner replications. \\}
\note{Then, the outer scenarios and inner sample means can be treated as features and labels for metamodel training. \\}
\note{Finally, instead of the inner sample mean from the standard procedure, the metamodel predictions estimate the portfolio loss and the risk measures. \\}
\note{Most existing works focus on the convergence rate of their estimators in terms of the simulation budget. \\}
\note{However, we find that there is a cost of pooling that comes from metamodel training, validation, and prediction. }

@@

\note{We start by comparing the asymptotic rates of different nested simulation procedures. \\}
\note{These are the convergence rates of the MSE of the risk measure estimator when the total simulation budget $\Gamma$ goes to infinity. \\}
\note{The standard procedure has the same convergence rate of $\mathcal{O}(\Gamma^{-2/3})$ for all types of $h$ considered. The rates in red are not available in the original works but are derived in this thesis. \\}
\note{The regression-based procedure has $\mathcal{O}(\Gamma^{-1})$ convergence rate for smooth and hockey-stick $h$. \\}
\note{It is achieved by only allowing $M$ to grow. In their experiments, $N$ is set to equal a constant. \\}
\note{The kernel smoothing procedure is the only procedure that depends on the asset dimension $d$. \\}
\note{When risk factor $X$ is high-dimensional, the kernel smoothing procedure may converge slower than the standard procedure. \\}
\note{The kernel ridge regression procedure and likelihood ratio procedure have the same convergence rate as the regression-based procedure. \\}
\note{However, in our numerical experiments, we find that their additional cost of pooling may offset their benefit of fast asymptotic rates. \\}
\note{Additionally for KRR, the authors analyze convergence of absolute error in probabilistic order instead of MSE.}

@@

\note{In most theoretical works, the focus is on the convergence rate of the MSE of the risk measure estimator. \\}
\note{However, for KRR, the authors analyze convergence of absolute error in probabilistic order. \\}
\note{One of the contributions of this thesis is to bridge the gap between MSE and absolute error convergence. \\}
\note{We first define the convergence in MSE and the convergence in probabilistic order. \\}
\note{And we show that the convergence rate of $\Gamma^{-\xi}$ in MSE of the risk measure estimator implies the convergence rate of $\Gamma^{-\frac{\xi}{2}}$ in probabilistic order. \\}
\note{We also show that the converse is not necessarily true.}

@@

\note{Previously, we worked on the asymptotic convergence rates of different nested simulation procedures. \\}
\note{In practice, the total simulation budget is finite.}
\note{When the budget is finite, the theoretical convergence rate may not be the only thing we should consider. \\}
\note{This figure shows the performance of all 5 procedures in their estimation of the quadratic tracking error for the portfolio of European call options.}
\note{It is a log-log plot of the MSE of the estimator versus the total simulation budget $\Gamma$.}
\note{For each procedure, we run 1000 macro replications of Monte Carlo simulations with different total simulation budgets. \\}
\note{For each data point on the plot, 1000 independent replications of the procedure are used to estimate the MSE. \\}
\note{The slopes of the lines estimates the empirical convergence rates of the procedures. \\}
\note{In the legend records the slopes of the lines and the corresponding asymptotic convergence rates of the procedures. \\}
\note{In the most basic case, most procedures have their empirical convergence rates match their asymptotic convergence rates. \\}
\note{However, as we will see after, this is not the case for all experiments. }

@@

\note{This figure shows the same experiment as the previous figure, but we further increase the asset dimension to 20. \\}
\note{The standard procedure is not affected by the asset dimension. \\}
\note{The kernel smoothing procedure actually converges faster than what its asymptotic convergence rate suggests. \\}
\note{The regression-based procedure is the only procedure that actually converges faster when the asset dimension is high. We will do a deeper dive into it in the following experiment. \\}
\note{It is also worth noting that the likelihood ratio and KRR procedures are dimension-independent. \\}
\note{While it is not shown in their empirical rate, due to their additional cost of pooling inner replications, we are not able to run these procedures when $\Gamma$ is large. \\}
\note{In the thesis, we provide a detailed analysis of the sensitivity for all 5 procedures with more than 500 experiments. }

@@

\begin{frame}{Conclusion}
    Regression-based nested simulation procedure:
    \begin{itemize}
        \item Most robust and stable for limited budgets
        \item Efficient to implement
        \item Fast empirical convergence for option portfolios
    \end{itemize}

@@

    \note{In our numerical experiemenct, we have shown that the regression-based procedure is the most cost-effective among all the procedures. \\}
    \note{It is robust and efficient to implement for limited budget sizes, and has fast empirical convergence for option portfolios. \\}
    \note{However, the regression-based procedure is not suitable for extremely high-dimensional risk factors or complex payoffs. \\}
    \note{The first reason is that it is hard to find a good regression basis for high-dimensional risk factors. It will involve a lot of feature engineering and expert knowledge. \\}
    \note{The second reason is that the regression-based procedure is not able to capture the nonlinearity in the payoff. \\}
    \note{In the next project, we will examine the performance of metamodel-based simulation procedures for variable annuities. \\}
    \note{This is where a neural network-based procedure can be more suitable as a form of automated feature engineering. }

@@

    \note{The main difference of the standard nested simulation of VAs can be explained by this illustration. \\}
    \note{This is how the P\&L is estimated for one outer scenario. \\}
    \note{It starts at $t=0$ with a simulation to estimate the initial value of the VA contract and the initial hedge. Here we are using delta-hedging. \\}
    \note{This hedge gets carried forward and updated at each time period with another simulation. \\}
    \note{The P\&L is then estimated by adding up the hedging error at each time period to the initial value of the VA contract. \\}
    \note{All the simulation mentioned is a single set of inner simulations for one outer scenario. \\}
    \note{It is very expensive to run this standard nested simulation for VAs. \\}

@@

\note{After numerical experiments, we find that the deep neural network metamodels are suitable for this problem. \\}
\note{We use LSTM for the sequential data. It provides accurate tail scenario identification and significant computational savings by budget concentration. \\}
\note{However, it is not transparent and interpretable. Many researchers are working on this topic. \\}
\note{This is where we can contribute to the research. \\}
\note{By using nested simulation as a data generating process, we can study the noise tolerance of DNNs. \\}
\note{The noise level in the training labels can be controlled by adjusting the simulation parameters. \\}
\note{By examining the performance of DNNs with different noise levels, we can provide direct evidence on the transparency and interpretability of DNNs. \\}

@@

\note{The two-stage procedure is a two-step process that is based on the idea of budget concentration. \\}
\note{First, we generate training data for the metamodel. \\}
\note{We use a fraction of the simulation budget to run the standard nested simulation procedure with $M$ outer scenarios and $N'$ inner replications. \\}
\note{We then train a metamodel using the feature-label pairs. \\}
\note{We use the trained metamodel to make predictions for all outer scenarios. \\}
\note{We then identify the predicted tail scenario set that contains the $m$ largest predicted losses. \\}
\note{Finally, we run the standard nested simulation procedure on the predicted tail scenarios. \\}

@@

\note{The single-stage procedure shares the same idea of running the standard nested simulation procedure to generate training data for the metamodel. \\}
\note{After a metamodel is trained, we use it to make predictions for VA contract losses accross all outer scenarios. \\}
\note{The risk measure is estimated using the predicted losses of the metamodel. \\}
\note{It is more efficient than the two-stage procedure because it avoids the second stage of the two-stage procedure. \\}
\note{It also avoids specifying a safety margin $m$, which is a feature of the two-stage procedure that we will discuss later.}

@@

    \note{We consider the following metamodel architectures: \\}
    \note{Multiple Linear Regression, Quadratic Polynomial Regression, Feedforward Neural Network, Recurrent Neural Network, and Long Short-Term Memory Network. \\}
    \note{Capacity is defined as the number of parameters in the metamodel. \\}
    \note{Higher capacity metamodels are more flexible and expressive. \\}
    \note{Lower capacity metamodels are less likely to overfit. \\}
    \note{The deep neural network metamodels are more flexible and expressive, but they are said to be more prone to overfitting. \\}
    \note{We will see whether this is indeed the case in our experiments. \\}

@@

    \note{We first take a look at their performance with QQ plots. \\}
    \note{On the left is the QQ plot between the true loss labels and the predicted loss labels for QPR, and on the right is the QQ plot for LSTM. \\}
    \note{Feature engineering for QPR is hardly feasible for our 240-dimensional $X$. Its poor performance is expected. \\}
    \note{DNN metamodels are more flexible, and they can make more accurate loss predictions. \\}

@@

\note{To further clarify our research questions, we consider the following scenario: \\}
\note{We have a noisy training data and a noisy test data. \\}
\note{We want to know what the metamodel learns from the noisy data. \\}
\note{We also want to know how well the metamodel can make accurate loss predictions for given scenarios. \\}
\note{In a simulation experiment, we can control the noise level in the training data and the test data. \\}
\note{We also have access to the true feature-label relationship when we increase the number of replications. \\}
\note{We can use this true feature-label relationship to evaluate the performance of deep neural networks, which is usually not possible in practice. }

@@

    \note{This table summarizes the results of our experiments. \\}
    \note{It is the most interesting finding that DNN metamodels with suitable architectures can \textbf{cut through the noise} in training labels. \\}
    \note{The average MSEs of metamodels on the training, test, and true data are reported in the three columns, respectively. \\}
    \note{Note that the training and test labels are noisy. The simulation noise is what makes them noisy, which is less present in the true data. \\}
    \note{First, we note that DNN metamodels has lower training errors than the traditional regression metamodels. \\}
    \note{This is expected because DNNs are more flexible and expressive than traditional regression metamodels. \\}
    \note{What is more interesting is the comparison between the test and true errors. \\}
    \note{We find that the true errors of RNN-based metamodels are lower than their test errors. \\}
    \note{This suggests that the RNN and LSTM metamodels can learn the true feature-label relationship. \\}
    \note{When we take another look at the table, we find that for LSTM, its true error is even lower than its training error. \\}
    \note{This is another evidence that LSTM metamodels are able to cut through the noise in training labels and fit to the true relationship. \\}
    \note{RNN metamodels suffer from the vanishing gradient problem. This is why we make separate rows for well-trained RNNs and poorly-trained RNNs. }

@@

    \note{For a two-stage procedure, we need to choose a safety margin $m$ to identify the tail scenarios. \\}
    \note{Consider estimating the $95\%$ CVaR with 100,000 outer scenarios. \\}
    \note{On the top is the true tail and non-tail scenarios, and on the bottom is the predicted tail and non-tail scenarios. \\}
    \note{The 5\% predicted tail scenarios are not guaranteed to contain all the true tail scenarios. \\}
    \note{Therefore, we need to add a safety margin $m$ to the predicted tail scenarios. \\}
    \note{On the bottom, we add a 2\% safety margin to the predicted tail scenarios. \\}
    \note{This adds 2,000 more scenarios to the inner simulations. \\}
    \note{We may add another 2\% safety margin to be more confident. \\}
    \note{This introduce a safety margin of $4\%$. $9000$ predicted tail scenarios are used for extensive inner simulations in stage 2. \\}
    \note{This is a trade-off between accuracy and efficiency. \\}
    \note{For a good metamodel, we only need a small safety margin to be accurate in tail identification. \\}
    \note{However, for a bad metamodel, the safety margin needs to be large to identify all the tail scenarios. \\}
    \note{This comes at the cost of more inner simulations, which is computationally expensive. \\}
    \note{So, one of the limitations of the two-stage procedure is the choice of safety margin. \\}
    \note{It can be partially mitigated by using a good metamodel. \\}

@@

    \note{We now consider the tail scenario identification and the CVaR estimation for the two-stage procedure. \\}
    \note{On the left is the tail scenario identification plot, and on the right is the plot of CVaR. \\}
    \note{We compare the two-stage procedure with the standard procedure. \\}
    \note{When colored lines cross the grey dashed line, it means that the metamodel is able to identify the tail scenarios as well as the standard procedure. \\}
    \note{And it should be able to estimate the CVaR as accurately as the standard procedure. \\}
    \note{We find that the LSTM metamodel is able to surpass the standard procedure on tail identification with a less than $5\%$ safety margin. \\}
    \note{However, the traditional regression metamodel is unable to identify the tail scenarios even with a high safety margin. \\}
    \note{A well-trained RNN is better than a FNN, but the poorly-trained RNN is far worse.}
    \note{The CVaR estimation plot shows similar results.}

@@

    \note{We now dig deeper into the research questions asked: how well do deep learning metamodels learn from noisy data? \\}
    \note{We study this phenomenon by considering the sensitivity testing for the DNN metamodels. \\}
    \note{The sensitivity of the DNN metamodels to the noise level in training labels and the number of training samples. \\}
    \note{In a simulation experiment, we can vary them to see how the DNN metamodels perform. \\}
    \note{We control the noise level in training labels by varying the number of inner replications $N'$. \\}
    \note{We control the number of training samples by varying the number of outer scenarios $M$. \\}
    \note{We consider two LSTM metamodels of different capacities because we want to see if the capacity of the metamodel matters for overfitting. \\}
    \note{The high-capacity LSTM metamodel has 10 times more parameters than the regular LSTM metamodel}

@@

    \note{This figure shows the CVaR estimates of the single-stage procedure. \\}
    \note{We compare it with the two-stage procedure using regular LSTM metamodel with no safety margin. So we are using the 5\% metamodel predicted tails to estimate the 95\% CVaR with extensive simulation in stage 2. \\}
    \note{The single-stage procedure with LSTM metamodels outperforms the two-stage procedure when noise level is moderate. \\}
    \note{Due to its design, the single-stage procedure is more efficient than the two-stage procedure. \\}
    \note{Setting $N' = 10$ is a reasonable budget allocation for the single-stage procedure. \\}
    \note{Further decreasing $N'$ to 1 deteriorates the performance of the single-stage procedure. But it is worth noting that the 2-stage procedure can overcome this issue by increasing the safety margin. \\}

@@

    \note{This figure shows the empirical convergence of the single-stage procedure with LSTM metamodels when only $M$ or $N'$ is varied. \\}
    \note{On the left, we fix $M=10^5$ and vary $N'$. \\}
    \note{There is no significant difference to further increase $N'$ when $N' \geq 10$. \\}
    \note{On the right, we fix $N'=10$ and vary $M$. \\}
    \note{We can see that the convergence rate is around $O(M^{-2/3})$. \\}
    \note{This finding is consistent with our previous analysis on the sensitivity of LSTM metamodels to data quality and data quantity. \\}
    \note{Once the quality is good enough, the quantity is more important. \\}

@@

\begin{frame}{Conclusion}

    \textbf{Key Findings:}
    \begin{itemize}
        \item   LSTMs are \textbf{resilient} to moderate levels of noise in training labels.
        \item   DNNs can learn \textbf{true} complex dynamic hedging model.
        \item   Two-stage procedure addresses regulatory concerns.
        \item   Single-stage procedure is \textbf{efficient}.
    \end{itemize}

@@

    \note{In this project, we present our extensive research into LSTM metamodels in a simulation setting.\\}
    \note{Our findings demonstrate that LSTMs can effectively learn complex hedging strategies even with noisy training data.\\}
    \note{The single-stage procedure offers an excellent balance of efficiency and accuracy for practical applications.\\}
    \note{We've shown that allocating computational budget to increase outer scenarios rather than inner simulations yields better results.\\}
    \note{These insights provide valuable guidance for implementing machine learning in financial risk management.\\}
    \note{For the research directions, we can apply deep neural network metamodels to other actuarial applications.\\}
    \note{We can also apply transfer learning to speed up the training process for deep neural network metamodels.\\}

@@

    \note{In this project, we propose a transfer learning framework for rapid adaptation of deep neural network metamodels in VA dynamic hedging.\\ }
    \note{The problem is the same as the previous project. We want to use deep neural network metamodels to approximate the complex simulation model that involves dynamic hedging.\\}
    \note{The difference is that we want to use transfer learning to speed up the training process.\\}
    \note{This can be beneficial for the practical applications.\\}
    \note{Firstly, new VA contracts are continuously issued.\\}
    \note{Secondly, market conditions are changing.\\}
    \note{Thirdly, the computational budget is limited.\\}
    \note{Transfer learning can help us to adapt to the new market conditions quickly and efficiently.\\}
    \note{We can pre-train the deep neural network metamodel on a large dataset of VA contracts with abundant simulation data.\\}
    \note{Then, we can fine-tune the metamodel on a smaller dataset of new VA contracts with limited data.\\}
    \note{The data is often limited for new VA contracts as simulation is expensive to run.\\}
    \note{The shared features between VA contracts can be leveraged to speed up the training process.\\}
    \note{We can also transfer the knowledge to other contract types.\\}
    \note{When a new VA contract is issued, we can use transfer learning to adapt the metamodel to the new contract quickly.\\}

@@

    \note{Transfer learning provides a formal framework for adapting models from one domain to another.\\}
    \note{The domain consists of a feature space and a probability distribution over that space.\\}
    \note{In our context, the feature space includes risk factors from the outer simulation.\\}
    \note{It is equipped with a probability distribution that describes the joint distribution of the risk factors.\\}
    \note{We don't know the exact joint distribution of the risk factors, but we can simulate outer scenarios from it using monte carlo simulation.\\}
    \note{The task consists of a label space and a predictive function mapping features to labels.\\}
    \note{For VA contracts, our labels are the contract losses under different scenarios.\\}
    \note{The source domain typically has abundant data - this could be existing VA contracts with extensive simulation data.\\}
    \note{The target domain has limited data - new VA contracts or existing contracts under new market conditions.\\}
    \note{Our goal is to leverage knowledge from the source domain to improve prediction in the target domain.\\}
    \note{This is particularly valuable when simulation data is expensive to generate for new contracts.\\}
    \note{The transfer learning approach allows us to maintain accuracy while significantly reducing computational requirements.}

@@

    \note{These figures further illustrate how source-target similarity affects transfer learning performance. \\}
    \note{The left graph shows transfer from no lapse models, which has slower convergence. \\}
    \note{The right graph shows transfer from static lapse models, with faster convergence. \\}
    \note{This reinforces our finding that greater similarity between source and target domains leads to more effective knowledge transfer. }

>>>>

\note{In the context of quantitative risk management, nested simulation is used for risk evaluation of financial derivatives and insurance products. \\}
\note{The nested structure is due to the loss random variable being a conditional expectation of the portfolio loss given the underlying risk factors. \\}
\note{In our problems, the 1-dimensional loss $L$ depends on the $d$-dimensional risk factors $X$. \\}
\note{Estimating a risk measure, $\rho(L)$, involves two levels of Monte Carlo simulations: a outer level generates underlying risk factors, and a inner level generates scenario-wise samples of portfolio losses. \\}
\note{The standard nested simulation procedure uses the inner sample mean under that scenario to estimate $L(X_i)$. \\}
\note{The nested structure makes the estimation computationally expensive. \\}
\note{In this thesis, we focus on examining and improving the efficiency of nested simulation procedures mostly by pooling with supervised learning metamodels.}

@@

\note{Pooling can happen in different ways, and the key idea is to use the information from different outer scenarios to improve the efficiency of nested simulation. \\}
\note{A supervised learning based procedure pools with these steps. \\}
\note{First, the user runs the standard procedure to generate a set of outer scenarios and inner sample means. \\}
\note{Then, they are treated as features and labels that train a metamodel. \\}
\note{Instead of using the inner sample mean, risk measures are estimated with the metamodel predictions. \\}
\note{Most existing works focus on the convergence rate of their estimators in terms of the simulation budget. \\}
\note{However, we find that there is a cost of pooling that comes from metamodel training, validation, and prediction. }

@@

\note{We start by comparing the asymptotic rates of different nested simulation procedures. \\}
\note{These are the convergence rates of the MSE when the total simulation budget $\Gamma$ goes to infinity. \\}
\note{The standard procedure has the same convergence rate of $\mathcal{O}(\Gamma^{-2/3})$ for all types of $h$ considered. The rates in red are not available in the original works but are derived in this thesis. \\}
\note{The regression-based procedure has $\mathcal{O}(\Gamma^{-1})$ convergence rate for smooth and hockey-stick $h$. \\}
\note{It is achieved by only allowing $M$ to grow. In their experiments, $N$ is set to equal a constant. \\}
\note{The kernel smoothing procedure is the only procedure that depends on the asset dimension $d$. \\}
\note{When risk factor $X$ is high-dimensional, the kernel smoothing procedure may converge slower than the standard procedure. \\}
\note{The kernel ridge regression procedure and likelihood ratio procedure have the same convergence rate as the regression-based procedure. \\}
\note{However, in our numerical experiments, we find that their additional cost of pooling is too high, which may offset their benefit of high asymptotic rates. \\}
\note{Additionally for KRR, the authors analyze convergence of absolute error in probabilistic order instead of MSE.}

@@

\note{In most theoretical works, the focus is on the convergence rate of the MSE of the risk measure estimator. \\}
\note{However, the analysis of KRR is different. \\}
\note{One of the contributions of this thesis is to bridge the gap between MSE and absolute error convergence. \\}
\note{We first define the convergence in MSE and the convergence in probabilistic order. \\}
\note{And we show that the convergence rate of $\Gamma^{-\xi}$ in MSE implies the convergence rate of $\Gamma^{-\frac{\xi}{2}}$ in probabilistic order. \\}
\note{We also show that the converse is not necessarily true.}

@@

\note{Previously, we worked on the asymptotic convergence rates of different nested simulation procedures. \\}
\note{In practice, the total simulation budget is finite.}
\note{When the budget is finite, these theoretical rates may not be the only thing we should consider. \\}
\note{This figure shows the performance of all 5 procedures in their estimation of the quadratic tracking error for the portfolio of European call options.}
\note{It is a log-log plot of the MSE of the estimator versus the total simulation budget $\Gamma$.}
\note{For each data point on the plot, 1000 independent replications of the procedure are used to estimate the MSE. \\}
\note{The slopes of the lines estimates the empirical convergence rates of the procedures. \\}
\note{In the legend records the slopes of the lines and the corresponding asymptotic rates. \\}
\note{In this case, most procedures have their empirical convergence rates matching their asymptotic rates. \\}
\note{However, as we will see after, this is not the case for all experiments. }

@@

\note{This figure shows the same experiment as the previous one, but we increase the asset dimension to 20. \\}
\note{The standard procedure is not affected by the asset dimension. \\}
\note{The kernel smoothing procedure actually converges faster than what its asymptotic convergence rate suggests. \\}
\note{The regression-based procedure is the only procedure that converges faster when the asset dimension is high. The reason is the regression-based procedure is particularly bad when we don't have enough data points at low $\Gamma$. We did a follow-up experiment to show regression converges in its asymptotic rate at high $\Gamma$. \\}
\note{Counter to what's on the graph, the likelihood ratio and KRR procedures are also sensitive to dimension. \\}
\note{While it is not shown in their empirical rate, due to their additional cost of pooling, we are not able to run these procedures when $\Gamma$ is large. \\}
\note{In the thesis, we provide a detailed analysis of the sensitivity for all 5 procedures with more than 500 experiments. }

@@

\begin{frame}{Future Work}
    Regression-based nested simulation procedure:
    \begin{itemize}
        \item Most robust and stable for limited budgets
        \item Efficient to implement
        \item Fast empirical convergence for option portfolios
    \end{itemize}

@@

    \note{Before here, we have shown that the regression-based procedure is the most cost-effective among all the procedures. \\}
    \note{It is robust and efficient to implement for limited budget sizes, and has fast empirical convergence for option portfolios. \\}
    \note{However, the it is not suitable for modeling variable annuities. \\}
    \note{It is hard to find a good regression basis for high-dimensional risk factors. It will involve a lot of feature engineering and expert knowledge. \\}
    \note{In the next project, we will design a metamodel-based simulation procedures for variable annuities. \\}
    \note{This is where a neural network-based procedure can be more suitable as a form of automated feature engineering. }

@@

    \note{The main difference of the standard nested simulation of VAs can be explained by this illustration. \\}
    \note{This is how the P\&L is estimated for one outer scenario. \\}
    \note{It starts at $t=0$ with a simulation to estimate the initial value of the VA contract and the initial hedge. Here we are using delta-hedging. \\}
    \note{This hedge gets carried forward and updated at each time period with another simulation. \\}
    \note{The P\&L is then estimated by adding up the hedging error at each time period to the initial value of the VA contract. \\}
    \note{All the simulation mentioned is a single set of inner simulations for one outer scenario. \\}
    \note{It is more expensive to run the standard nested for VAs. \\}

@@

\note{After some numerical experiments, we found that the deep neural network metamodels are suitable for this problem. \\}
\note{We use LSTM for the sequential data. It can predict tail scenarios accurately, so we can use it to concentrate simulation budget on the tail scenarios. \\}
\note{However, it is not transparent. Many researchers are working on this topic. \\}
\note{This is where we can contribute to the field. \\}
\note{By using nested simulation as a data generating process, we can study the noise tolerance of DNNs. \\}
\note{We can control data quality and quantity by adjusting the simulation parameters. \\}
\note{By examining the performance of DNNs, we can provide direct evidence on the transparency of DNNs. }

@@

\note{Our two-stage procedure is based on the idea of budget concentration. \\}
\note{In stage 1, we use a fraction of the simulation budget to run the standard nested simulation procedure. \\}
\note{We then train a metamodel using the scenarios and the inner sample means. \\}
\note{We use metamodel predictions to identify the tail scenario set that contains the $m$ largest predicted losses. \\}
\note{In stage 2, we run the standard nested simulation procedure on these predicted tail scenarios. \\}

@@

    \note{In our experiments, we found some DNN metamodels that can make accurate loss predictions, so we propose a single-stage procedure. \\}
    \note{It shares the same idea of running the standard nested to get training data. \\}
    \note{After a metamodel is trained, the risk measure is estimated using the metamodel predictions directly. \\}
    \note{It is more efficient than the two-stage procedure because it avoids the stage 2 of the two-stage procedure. \\}
    \note{It also avoids specifying a safety margin $m$, which is a feature of the two-stage procedure that we will discuss later.}

@@

    \note{We consider the following metamodel architectures: \\}
    \note{Multiple Linear Regression, Quadratic Polynomial Regression, Feedforward Neural Network, Recurrent Neural Network, and Long Short-Term Memory Network. \\}
    \note{Capacity is defined as the number of parameters in the metamodel. \\}
    \note{Lower capacity metamodels are less likely to overfit. \\}
    \note{The deep neural network metamodels are higher in capacity, but they are said to be more prone to overfitting. \\}
    \note{We will see whether this is indeed the case in our experiments. \\}

@@

    \note{We first take a look at their performance with QQ plots. \\}
    \note{On the left is the QQ plot between the true loss labels and the predicted loss labels for QPR, and on the right is the QQ plot for LSTM. \\}
    \note{Feature engineering for QPR is hardly feasible for our 240-dimensional $X$. Its poor performance is expected. \\}
    \note{DNN metamodels are more flexible, and they can make more accurate predictions. \\}

@@

\note{To further clarify our research questions, we consider the following scenario: \\}
\note{We have noisy training data and noisy test data. \\}
\note{We want to know what the metamodel learns from the noisy data. \\}
\note{We also want to know how well the metamodel can make accurate predictions. \\}
\note{In a simulation experiment, we have control over the noise level in the training data and the test data. \\}
\note{We also have access to the true relationship when we increase the number of replications. \\}
\note{We can use this true relationship to evaluate the performance of deep neural networks, which is usually not possible in practice. \\ }
\note{Instead of measuring the distance between the blue line and the orange dots, we can measure the distance between the blue line and the red line. }

@@

    \note{This table summarizes the results of our experiments. \\}
    \note{It is the most interesting finding that DNN metamodels with suitable architectures can \textbf{cut through the noise} in training labels. \\}
    \note{The average MSEs of metamodels on the training, test, and true data are reported in different colors. \\}
    \note{Note that the training and test labels are noisy due to simulation noise. This noise is less present in the true labels. \\}
    \note{First, we note that DNN metamodels has lower training errors than the traditional regression metamodels. \\}
    \note{This is expected because DNNs are more flexible. \\}
    \note{What is more interesting is the comparison between the test and true errors. \\}
    \note{We find that the true errors of RNN-based metamodels are lower than their test errors. \\}
    \note{This suggests that the RNN and LSTM metamodels can learn the true feature-label relationship. \\}
    \note{When we take another look at the table, we find that for LSTM, its true error is even lower than its training error. \\}
    \note{This is another evidence that LSTM metamodels are able to cut through the noise in training labels and fit to the true relationship. \\}
    \note{RNN metamodels suffer from the vanishing gradient problem. This is why we make separate rows for well-trained RNNs and poorly-trained RNNs. }

@@

    \note{Coming back to the two-stage procedure, we need to choose a safety margin $m$ to identify the tail scenarios. \\}
    \note{Consider estimating the $95\%$ CVaR with 100,000 outer scenarios. \\}
    \note{On the top is the true tail and non-tail scenarios, and on the bottom is the predicted tail and non-tail. \\}
    \note{The 5\% predicted tails are not guaranteed to contain all the true tails. \\}
    \note{Therefore, we need to add a safety margin $m$. \\}
    \note{On the bottom, we add a 2\% safety margin. \\}
    \note{This adds 2,000 more scenarios to the inner simulations. \\}
    \note{We may add another 2\% safety margin to be more confident. \\}
    \note{This introduce a safety margin of $4\%$. In total, $9000$ predicted tails are used for extensive inner simulations in stage 2. \\}
    \note{This is a trade-off between accuracy and efficiency. \\}
    \note{For a regression metamodel, the safety margin needs to be large to identify all the tail scenarios. \\}
    \note{This comes at the cost of more inner simulations, which is computationally expensive. \\}
    \note{So, one of the limitations of the two-stage procedure is the choice of safety margin. \\}
    \note{It can be partially mitigated by using a good metamodel. \\}

@@

    \note{We now consider the precentage of tail match and the CVaR estimates for the two-stage procedure. \\}
    \note{On the left is the tail match plot, and on the right is the plot for CVaR. \\}
    \note{We compare the two-stage procedure with the standard procedure. \\}
    \note{When colored lines cross the grey dashed line, it means that the metamodel is able to identify the true tails as well as the standard procedure. \\}
    \note{And it should be able to estimate the CVaR as accurately. \\}
    \note{We find that the LSTM metamodel is able to surpass the standard procedure on tail identification with a less than $5\%$ safety margin. \\}
    \note{However, the traditional regression metamodel is unable to identify the tail scenarios even with a high safety margin. \\}
    \note{They are not even in the first plot. \\}
    \note{A well-trained RNN is better than a FNN, but the poorly-trained RNN is far worse.}
    \note{The CVaR plot shows similar results.}

@@

    \note{We now dig deeper into the research questions asked: how well do deep learning metamodels learn from noisy data? \\}
    \note{We study this phenomenon by testing the sensitivity of the DNN metamodels to the noise level in training labels and the number of training samples. \\}
    \note{In a simulation experiment, we have the flexibility to vary them. \\}
    \note{Data quality is controlled by $N'$, and data quantity is controlled by $M$. \\}
    \note{We consider two LSTM metamodels of different capacities. \\}
    \note{The high-capacity LSTM has 10 times more parameters than the regular LSTM.}

@@

    \note{This figure shows the CVaR estimates of the single-stage procedure. \\}
    \note{We compare it with the two-stage procedure using regular LSTM metamodel with no safety margin. So we are using the 5\% metamodel predicted tails to run extensive simulation in stage 2. \\}
    \note{The single-stage procedure with LSTM metamodels outperforms the two-stage procedure when noise level is moderate. \\}
    \note{Due to its design, the single-stage procedure is more efficient than the two-stage procedure. \\}
    \note{Setting $N' = 10$ is a reasonable budget allocation for the single-stage procedure. \\}
    \note{Further decreasing $N'$ to 1 deteriorates the performance of the single-stage procedure. But it is worth noting that the 2-stage procedure can overcome this issue by increasing the safety margin. \\}

@@

    \note{This figure shows the empirical convergence of the single-stage procedure with LSTM metamodels when only $M$ or $N'$ is varied. \\}
    \note{On the left, we fix $M=10^5$ and vary $N'$. \\}
    \note{There is no significant difference to further increase $N'$ when $N' \geq 10$. \\}
    \note{On the right, we fix $N'=10$ and vary $M$. \\}
    \note{We can see that the convergence rate is around $O(M^{-2/3})$. \\}
    \note{This finding is consistent with our previous analysis on the sensitivity of LSTM metamodels to data quality and data quantity. \\}
    \note{Once the quality is good enough, the quantity is more important. }

@@

\begin{frame}{Future Directions}

    \textbf{We have found that:}
    \begin{itemize}
        \item   DNNs can learn \textbf{true} complex dynamic hedging model.
    \end{itemize}

@@

    \note{In this project, we demonstrate that LSTMs can effectively learn complex hedging strategies even with noisy training data.\\}
    \note{We can apply deep neural network metamodels to other actuarial products.\\}
    \note{However, DNNs are data-hungry. We may not have enough time to simulate enough data for new products.\\}
    \note{That's where transfer learning can help us to speed up the training process for contracts with not enough data.}

@@

    \note{In this project, we propose a transfer learning framework for rapid adaptation of deep neural network metamodels in VA dynamic hedging.\\ }
    \note{The problem is the same as the previous project. We want to use deep neural network metamodels to approximate the complex simulation model that involves dynamic hedging.\\}
    \note{The difference is that we want to use transfer learning to speed up the training process when the amount of data is limited.\\}
    \note{This can be beneficial for the practical applications.\\}
    \note{Firstly, new VA contracts are continuously issued.\\}
    \note{Secondly, the computational budget is limited for simulation.\\}
    \note{With transfer learning, we can pre-train the deep neural network metamodel on a large dataset of VA contracts with abundant simulation data.\\}
    \note{Then, we can fine-tune the metamodel on new VA contracts with limited data.\\}
    \note{The shared features between VA contracts can be leveraged to speed up the training process.\\}
    \note{We can also try transferring knowledge to other contract types.}

@@

    \note{Transfer learning provides a formal framework for adapting models from one domain to another.\\}
    \note{The domain consists of a feature space and a probability distribution over that space.\\}
    \note{In our context, the feature space includes risk factors from the outer simulation.\\}
    % \note{It is equipped with a probability distribution that describes the joint distribution of the risk factors.\\}
    \note{We don't know the exact joint distribution of the risk factors, but we can simulate outer scenarios from it using monte carlo simulation.\\}
    \note{The task consists of a label space and a predictive function mapping features to labels.\\}
    \note{For a VA dynamic hedging problem, our labels are the contract losses for different scenarios.\\}
    \note{The source domain typically has abundant data - this could be existing VA contracts with extensive simulation done already.\\}
    \note{The target domain, new VA contracts may have limited data.\\}
    \note{Our goal is to leverage knowledge from the source domain to improve performance in the target domain.\\}
    \note{This is particularly valuable when simulation data is expensive to generate for new contracts.\\}
    \note{It allows us to maintain accuracy while significantly reducing computational requirements.}

@@

    \note{These figures further illustrate the same idea. \\}
    \note{The left graph shows transfer from no lapse models, which has slower convergence. \\}
    \note{The right graph shows transfer from static lapse models, with faster convergence. \\}
    \note{This reinforces our finding that greater similarity between source and target domains leads to more effective knowledge transfer. }
